Evaluating machine translation for assimilation via a gap-filling task

### 2015-04-04 2015-eamt-assim/2015-eamt-assim.tex
More corrections by reviewers' comments
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59620 72bbbca6-d526-0410-a7d9-f06f51895060

\newcommand{\comment}[1]{\marginpar{\scriptsize\sf \textcolor{blue}{#1}}}
%\newcommand{\comment}[1]{}
\newcommand{\blankout}[1]{\phantom{#1}} % anonymous
%\newcommand{\blankout}[1]{#1} % non-anonymous

@@

% a little on categories
\subsection{Results for different domains}
For the Tatar--Russian language pair the participants were offered texts from three different domains (in equal proportions): casual conversations, legal texts and news. The results by domains are displayed in tables \ref{table:rus-casual}, \ref{table:rus-legal}, and \ref{table:rus-news}. The MT system used in the evaluation has been targeted to translate texts from all three of the domains. Taking into consideration the above discussion of 10\% MT+Source tasks, we observe similar results across the three categories. Note that, in casual and news texts, the source sentences paired with MT significantly improve participants' performance compared to MT-only task mode. This may be due to the fact that many words are borrowed from Russian into Tatar, and are in fact understood by Russian speakers.

@@

\phantom{This work has been partly funded by the Spanish Ministerio de Econom{\'i}a y Competitividad through project TIN2012-32615 and by the Google Summer of Code 2014 programme. We would like to thank the volunteers who participated in the evaluations.}

>>>>

%\newcommand{\comment}[1]{\marginpar{\scriptsize\sf \textcolor{blue}{#1}}}
\newcommand{\comment}[1]{}
%\newcommand{\blankout}[1]{\phantom{#1}} % anonymous
\newcommand{\blankout}[1]{#1} % non-anonymous

@@

% a little on categories
\subsection{Results for different domains}
For the Tatar--Russian language pair the participants were offered texts from three different domains (in equal proportions): casual conversations, legal texts and news. The results by domains are displayed in tables \ref{table:rus-casual}, \ref{table:rus-legal}, and \ref{table:rus-news}. The MT system used in the evaluation has been targeted to translate texts from all three of the domains. Taking into consideration the above discussion of 10\% MT+Source tasks, we observe similar results across the three categories. Note that the source sentences paired with MT improve participants' performance in casual texts, compared to MT-only task mode. This may be due to the fact that many words are borrowed from Russian into Tatar, and are in fact understood by Russian speakers.

@@

This work has been partly funded by the Spanish Ministerio de Econom{\'i}a y Competitividad through project TIN2012-32615 and by the Google Summer of Code 2014 programme. We would like to thank the volunteers who participated in the evaluations.
